\section{Limits and Compact Sets}

\subsection{Limits In $\mathbb{C}$}

\begin{defn}[\textbf{Open Disc of radius $r > 0$ centered at $\alpha$}]
	The set $S \subset \mathbb{C}$ with elements $z$ such that:
	\[ |z - \alpha | < r \]
	Denoted $D(\alpha, r).$
\end{defn}

\begin{defn}[\textbf{Open Set $U \subset \mathbb{C}$}]
	$U$ is an open set if for every point $\alpha \in U$:
	\begin{enumerate}
		\item there is a disc $D(\alpha,r)$ centered at $\alpha$
		\item there is a disc of some radius $r > 0$ such that this disc $D(\alpha, r)$ is contained in $U.$
	\end{enumerate}
\end{defn}

\begin{defn}[\textbf{Boundary Point of $S$}]
	A point $\alpha$ such that every disc $D(\alpha, r)$ centered at $\alpha$ and of 
	radius $r > 0$ contains both points of $S$ and points not in $S.$
\end{defn}

\begin{defn}[\textbf{Adherent Point to $S$}]
	$\alpha$ is adherent to $S$ if: 
	\begin{itemize}
		\item every disc $D(\alpha, r)$ with $r > 0$ contains \textit{some} element of $S.$
	\end{itemize}
\end{defn}

\begin{defn}[\textbf{Interior point to $S$}]
	$\alpha$ is an interior point of $S$ if:
	\begin{itemize}
		\item there exists a disc $D(\alpha, r)$ which is contained in $S.$
	\end{itemize}
\end{defn}

Note that:
\begin{itemize}
	\item An adherent point can be a boundary point
	\item An adherent point can be an interior point
\end{itemize}

\begin{defn}[\textbf{Closed Set}]
	A set is closed if it contains all its boundary points.
\end{defn}

\begin{defn}[\textbf{Bounded Set}]
	$S$ is bounded if there exists a number $C > 0$ such that:
	\begin{align*}
		|z| \leq C \;\;\;\;\; \forall z \in S
	\end{align*}
\end{defn}

\begin{defn}[\textbf{Closure of a Set $S$}]
	The unioin of $S$ and all its boundary points.
	\begin{itemize}
		\item Denoted $\bar{S}$
	\end{itemize}
\end{defn}

\begin{defn}[\textbf{Limit of $f$}]
	
\end{defn}
\begin{itemize}
	\item Let $f$ be a function on $S \subseteq \mathbb{C}.$ 
	\item Let $\alpha$ be an adherent point of $S.$ 
	\item Let $w$ be a complex number. 
\end{itemize}
Say that:
	\[ z \in S \]
	\[ \lim_{z \to \alpha} f(z) = w \]
If given $\epsilon > 0$ there exists $\delta > 0$ such that if $z \in S$ and $|z - \alpha| < \delta,$ then:
\[ |f(z) - w | < \epsilon \]

\begin{defn}[\textbf{Continuous}]
	$f$ is continuous at $\alpha$ if:
	\[ \lim_{z \to \alpha} f(z) = f(\alpha) \]
\end{defn} 

\begin{defn}[\textbf{Cauchy Sequence}]
	If $\epsilon > 0$ then $\exists \; N$ such that if:
	\[ m, n \geq N \]
	then:
	\[| \; {z}_{n} - {z}_{m} \; | < \epsilon \]
\end{defn}

\subsection{Compact Sets}
This section is a bit peculiar and full of theorems I've not had a use for yet, but may be useful later. The main point is this:
\begin{thm}
	A set $S$ is compact $\iff$ it is closed and bounded.
\end{thm}

\subsection{Sequence of Complex Numbers (My own section)}

\begin{defn}[\textbf{Sequence of Complex Numbers}]
	A function defined on the set of Natural numbers whose 
	range is contained in the set of Complex numbers.
	\[n \to z\]
\end{defn}

If a sequence has a limit, it converges. Else, it diverges.

\newpage